Compositional Quantitative Resource Analysis of C Programs

### 2014-06-24 paper/main.tex
more on the soundness

We can now define the \emph{semantic validity} of a function-context
free logic judgement $B; R \vdash \htriple P S Q$ as follows
\begin{align*}
\valid n B R P S Q := \\
\forall m\, \cont .\,& (m \le n \land \safeK m B R Q \cont) \\
&\implies \safe m P S \cont.
\end{align*}
We use this validity definition to give a meaning to function
specifications $\forall z \, \vec v \, v.(P_f \, z \, \vec v,
Q_f \, z \, v)$ as follows
$$
  \forall z \, \vec v \, n .\,
  \valid n \bot {Q_f \, z} {P_f \, z \, \vec v} {S_f} \bot ,
$$
where $S_f$ is the body of the function $f$.

>>>>

We can now define the \emph{semantic validity} of a logic judgement
$B; R \vdash \htriple P S Q$ without function context as follows
\begin{align*}
&\valid n B R P S Q := \\
&\qquad \forall m \, \cont \, x .\, (m \le n \land \safeK m {B+x} {R+x} {Q+x} \cont) \\
&\qquad \implies \safe m {P+x} S \cont.
\end{align*}
Note how the validity of a triple embeds the frame rule of
our logic, this refinement is necessary to have a stronger
induction hypothesis available during the proof.

Using this semantic validity  we can define the validity of
a function context $\Delta$ that we write $\validC n \Delta$ as
\begin{align*}
  &\forall f .\, \Delta(f) =
    \forall z \, \vec v \, v .(P_f \, z \, \vec v, Q_f \, z \, v)
    \implies \\
  &\qquad \forall z \, \vec v .\,
  \valid n \bot {Q_f \, z} {P_f \, z \, \vec v} {S_f} \bot ,
\end{align*}
where $S_f$ is the body of the function $f$.

\begin{theorem}[Soundness of the logic]
  If $\Delta; B; R \vdash \htriple P S Q$ is derivable, then
  $$
    \forall n .\, \validC n \Delta
      \implies \forall n .\, \valid n B R P S Q.
  $$
\end{theorem}
